An Image-based method for phase estimation, gating and temporal super-resolution of \\cardiac ultrasound

### 2017-02-21 paper155.tex
Started writing the introduction section

%\vspace{-0.5cm}
\section{Introduction}
\label{sec:intro}
%
Cardiovascular disease is the leading cause of death worldwide and ultrasound is emerging as an increasingly effective tool for rapid non-invasive visual assessment of cardiac structure and function. 
%

>>>>

%\vspace{-0.5cm}
\section{Introduction}
\label{sec:intro}
%
Cardiovascular disease is the leading cause of death worldwide and ultrasound is emerging as an increasingly effective tool for rapid non-invasive visual assessment of cardiac structure and function. Two kinds of periodic motion are present in cardiac ultrasound videos, one that corresponds to the beating heart motion and the other that corresponds to respiratory motion. Knowing the phase or location of each video frame within the cardiac and/or respiratory cycles is essential in a variety of applications. 
Cardiac motion is usually tracked by simultaneously acquiring an ECG signal and respiratory motion is tracked through the motion of markers placed on the subject's body.
%
